Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and it's audio-description

### 2020-04-30 paper/main.tex
minor revisions

\documentclass[english]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{babel}
\usepackage{svg}
\usepackage{caption, booktabs}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{todonotes}
\usepackage[
	colorlinks=true,
	urlcolor=blue,
	linkcolor=green
]{hyperref}
\newcommand{\scidatalogo}{\includegraphics[height=36pt]{SciData_logo.jpg}}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\setlength{\headheight}{40pt}
\lhead{\textsc{\scidatalogo}}
\usepackage{natbib}

\begin{document}

@@

\todo[inline]{Vorgabe: Intro + Discussion = main text ~ 3,000 words}

@@

Cognitive neuroscientists use brain imaging methods like blood oxygenation level-dependent functional magnetic resonance imaging (BOLD fMRI) to map perceptual and cognitive brain processes (e.g. viewing of landscapes, \citep{epstein1998ppa}; or theory of mind \citep{spunt2014validating}) to functional brain areas or networks. Brain mapping studies have traditionally employed small sets of carefully chosen, simplified stimuli to strictly control experimental conditions and facilitate functional isolation of brain areas.

@@

Additionally, brain mapping studies have traditionally averaged / usually average results across at least 10-15 subjects to improve the signal-to-noise-ratio (SNR). The disadvantage here is that the averaging approach does not  characterize brain functions at an individual level, a prerequisite for the application of brain imaging methods in individual diagnostics (cf. \citep{dubois2016building})

@@

\todo[inline]{Egal, was ich folgend in der Überblick \& später im Detail bzgl. Aziz (2008) schreibe, es wird wahrscheinlich nicht korrekt sein; so wie ich es verstanden habe, hat Aziz den Unterschied zwischen PPA und FFA abgeguckt, aber diesen Unterschied im Kontrast zu object-related Sentences; s. dortige Fig 3; im Grunde kommt da aber überall nur uneinheitliche Grütze raus}

@@

% Aziz hat auf eine zweite Mail geantwortet: Sie hat kein Block-Design, sondern modelt die HRF über den jeweils gesamten Satz von ca. 2.8 Sekunden.
% wie oben im Kommentar erwähnt: Ihre Method Section halte ich für etwas strange.Ich zeige dir ganz am Ende mal ihr Paper; hab die entsprechenden Stellen annotiert. Sonst wird hier im Detail Mist erzählt
To our knowledge only one study by \citep{aziz2008modulation} correlated hemodynamic activity of the PPA with spoken sentences. Sentences described generic or famous places (e.g. ``The Taj Mahal faces a long thin reflecting pool'') or faces  (e.g. ``Marylin Monroe has a large square jaw''). Participants were instructed to press a button whenever the sentence described an inaccurate or improbable fact. Surprisingly, activation in the left, but not right, PPA was significantly reduced when participants listened to place-related sentences compared to listening to face-related sentences. Moreover, this effect was only observed in sentences involving famous places.

\todo[inline]{Review von Aminoff (2013) kommt nur kurz als "competing hypothesis"; muss man dann natürlich in der Discussion diskutieren; was aber ggf. gar nicht notwendig ist, weil's darum gar bei uns gar nicht geht}
In summary, studies suggest that the PPA does not exclusively respond to visual(ly) spatial information. This is consistent with a competing hypotheses stating the PPA does not process the spatial layout of a scene specifically but contextual associations in general \citep{aminoff2006parahippocampal} for a review). Independent(ly) from competing theories (s. \citep{aminoff2013role} for a review), it is still unacknowledged/ uncertain/ indeterminate if auditory stimuli lead to inhibitory or excitatory responses, or no change at all in the PPA.
\todo[inline]{Coolnessfaktor von naturalistic stimuli ist beinahe komplett raus; Data-driven vs. theory-driven analyses ist komplett raus -> vgl. Speech-Anno-Paper; jedoch in Discussion bringen (s. dort); ggf. erwähnen, dass möglichst ähnliche und nicht fancy analysis gewählt wurde, um Replizierung der Ergebnisse, aber mit naturalistic stimuli zu gewährleisten.}
All revied studies used a just a small set of carefully designed, simplified stimuli to strictly control experimental conditions. They further relied on / implemented explicit judgment-based tasks to keep participants alert and paying attention. Thus, they cannot / could answer the question how the PPA might behave under life-like conditions.
Naturalistic stimuli like movies \citep{hasson2008neurocinematics, sonkusare2019naturalistic} or narratives \citep{honey2012not, lerner2011topographic, silbert2014coupled} offer an easy to implement, (continuous,) complex, immersive stimulus that better resembles our experience of a continuous dynamic environment.
Two early studies using naturalistic stimuli suggest functional specialization is preserved during free viewing of a movie when many areas respond simultaneously and interact [<- der Schlusssatz ist aus hasson und bartels plagiiert \citep{bartels2004mapping, hasson2004intersubject}

% Bartels (2004) und Hasson (2004)
\citep{bartels2004mapping} manually annotated time points that depict faces and human bodies in a 22 minute clip of the movie \textit{Tomorrow Never Dies}.
Employing a general linear model to model hemodynamic activity, these time points correlated with increased activity in the ``fusiform face area'' \citep{kanwisher1997ffa} and ``extrastriate body area'' \citep{downing2001bodyarea} respectively. Employing a reverse intersubject correlation, \citep{hasson2004intersubject} took used a 30 minute clip of the movie \textit{The Good, the Bad, the Ugly}.
fMRI brain volumes showing the highest hemodynamic activity in the PPA [across (five) participants] were matched to the (temporally) correlating movie frames.
Results revealed that frames depicted indoor and outdoor scenes including buildings and open fields.
Nevertheless, no study investigated how the PPA responds to spatial clues that are embedded in a complex, audio-only stimulus.

% Bzgl. Open Source der der Ergebnisse/Skripte: Dazu habe ich hier nichts geschrieben, weil ich nur weiß, das der Code veröffentlicht werden soll. Du hast die Vision diesbezüglich im Kopf und entsprechend auch kanonisch-prägnante Formulierungen und wo die am besten wie hinkommen

% Präteritum oder Präsens? Ist momentan gemischt; find's ok so.
% N=14 is inner join of AV & AO
\todo[inline]{The next paragraphs contain a bunch of methods already; reduce this to talk about the general approach:
    a) annotation of events,
    b) investigation of model quality,
    c) cross-analysis of datasets.
    d) Possibly cite https://psyarxiv.com/sdbqv/
    and declare that this study is a concrete realization of that promise
}
In this study, we analyze data of three publicly available datasets from the same set of 14 participants as part of the studyforrest data set (\href{http://www.studyforrest.org}{studyforrest.org}).
We exploratorily investigate how the parahippocampal gyrus [or more general ``human brain''?] responds to ``spatially relevant'' events embedded in a 2h audio-visual movie \citep{hanke2016simultaneous} and its audio-description of the same length \citep{hanke2014audiomovie}.
We compare these results to PPA localizations that were obtained from a dedicated visual localizer experiment \citep{sengupta2016extension}.
Both natural stimuli were originally designed to entertain an audience and to capture attention free from any perceptual or behavioral task.
We annotated events in the otherwise unknown temporal structure of both stimuli.
In/for the movie, we annotated different kinds of cinematographic cuts \citep{haeusler2016cutanno} as presumably ``spatially relevant'' events.
Our rationale was that cuts re-orient the viewer in the depicted environment independent from the exact visual content in the movie frame following the cut.
In/for the audio-description, we annotated verbal clues about the missing visual content given by the audio-description's additional narrator \citep{haeusler2020speechanno}.
In conformity to the analyses performed in the studies using not-naturalistic stimuli, we employed a standard multi-level, voxel-wise general linear model (GLM) % in order to???
% Practical reasons = Es war viel einfacher nouns der audio-description als Frameinhalt des Films zu annotieren
For practical reasons, and encouraged by \citep{aziz2008modulation} and \citep{aminoff2013role}, we focus on the audio-description as a possible life-like stimulus free from any task to localize a ``visual area'' in individual study participants.

\section{Methods}
\todo[inline]{Specific data outputs should be explicitly referenced via data citation (see Data Records and Data Citations, below)}
\todo[inline]{MIH: we should consider making a statement how often these datasets have been analyzed be independent groups already -> Frage: ist die Liste auf psychoinformatics.de ist aktuell/erschöpfend? Ist dann schnell eingebaut}
\todo[inline]{entsprechend der neuen Infos hier, oben das Ende der Einleitung kürzen}
We used data from three publicly available datsets as part of the studyforrest dataset (\href{http://www.studyforrest.org}{studyforrest.org}) that has already been used by other research groups for independent research questions before. We used fMRI data from 14 subjects who took part in three different studies. Namely the same subjects were
a) listening to the audio-description (AO study) \citep{hanke2014audiomovie}) of the movie ``Forrest Gump'', a dataset already used by [XY].
b) watching the actual audio-visual movie (AV study) \citep{hanke2016simultaneous}, a dataset already used by [XY].
c) participating in a dedicated block-wise visual localizer (LOC study) \citep{sengupta2016extension}, a dataset aready used by [XY]. An exhaustive description of the participants, stimulus creation, procedure, stimulation setup, and fMRI acquisition can be found in the corresponding publications  \citep{hanke2014audiomovie, hanke2016simultaneous, sengupta2016extension}. Following is a brief summary of most important aspects.
\todo[inline]{Fokus des gesamten Methodenteils liegt auf den Naturalistic Stimuli; LOC study ist bisher effektiv nicht mit drin}

\subsection{Participants}
% ich habe von den aligned data eine Intersection of 14 VPN von AO und AV
% in der Speech-Anno-Validation (AO only) habe ich 19 VPN
% es fehlt jeweils VP10
In the AO study, twenty [+++also, ich habe nur Daten von 19 benutzt; VP10 hat keine (aligned) Daten+++] participants (all right-handed, age 21–38 years, mean age 26.6 years, 12 male) listened to the German audio-description \citep{ForrestGumpGermanAD} of the movie ``Forrest Gump'' \citep{ForrestGumpMovie} as an additional audio track for visually impaired listeners on Swiss public television.
In the AV study, the same 15 participants [+++VP 10 wurde entpsrechend nicht genutzt+++] (21–39 years, mean age 29.4, six female) watched the audio-visual movie with dubbed German audio track \citep{ForrestGumpDVD}.
% LOC study einarbeiten
In the LOC study [].

@@

\subsection{Stimuli}
The movie's  \citep{ForrestGumpMovie} audio track and the audio-description \citep{ForrestGumpGermanAD} are largely identical.The plot is carried by an off-screen voice of the main character Forrest Gump.
The audio-description's male narrator additionally verbalizes essential aspects of the visual scenery when there is no dialog, off-screen voice or relevant sound in the audio track.
The audio-description was temporally aligned to the audio track of the German DVD release. A few scenes less relevant to the major plot were removed to create the ``research cut'' lasting $\approx$2h. Both stimuli were further processed (filtering, volume adjustments) to improve understandability / audibility during MRI scanning.
Finally, each stimulus was split into eight segments of approximately 15 minutes. Except for the first movie segment, each segment started with a snippet of at least six seconds immediately preceding the movie scene boundary used to split the segments (s. Figure 3a in \citep{hanke2014audiomovie}
% LOC study?

\subsection{Stimulus Annotation}
\todo[inline]{einleitendes Blabla zu haeusler2020speechanno}
\todo[inline]{allg. überarbeiten; deutlich machen, WARUM WAS WIE annotiert wurde}
% Florian hat 2 Regeln falsch verstanden, sonst war übereinstimmung 90-95%
% Kategorie ``++'' enthält ausnahmesweise auch adverbiale Best. der Zeit.
% ggf. angeben, dass die effektiv identisch waren
\todo[inline]{aus Speech-Anno Paper 'descriptive-statistics-anno.py' übernehmen \& anpassen, um Statistiken und runcommand-file zu erstellen}
A further annotation of the audio-description's narrator was done manually: Two
persons performed a categorization of nouns embedded in sentences spoken by the
narrator to describe the movie's missing visual content.
Categories focus on the cinematographic scene's environment, inherent objects, persons, and a person's appearance (cf. table \ref{tab:descr-nouns})..
A categorizing of nouns that serve as auditory cues about the movie's visual content. Comprised categories focus on the cinematographic scene's environment (geo, geo-room; setting\_new, setting\_old), inherent persons (female, female name; male, male name, person), their appearance (face, head; body, bodypart), and objects (object, furniture).
The nouns are categorized by the clue they provide about a cinematographic scene's environment \todo{maybe skip the names and just cite the table} (geo, geo-room; setting\_new, setting\_rec), its inherent persons (female, female name; male, male name, person), a person's appearance (face, head; body, bodypart), and a scene's inherent objects (object, furniture).
A preliminary annotation according to the rules [entweder im laufenden Text oder in Tabelle], einer neuen Tabelle oder im laufenden Text was done by one person and corrected in several runs by the author.

@@

\subsection{Stimulation setup}
\todo[inline]{irrelevantes kürzen}
In both studies, stimulation was implemented with PsychoPy v1.79 (with an early version of the MovieStim2 component later to be publicly released with \href{http://www.psychopy.org}{PsychoPy v1.81}; \citep{peirce2007psychopy}) running on a computer with the \href{http://neuro.debian.net}{(Neuro)Debian} operating system \citep{halchenko2012open}.
In the AO study, visual instructions were presented on a rear-projection screen inside scanner bore using an LCD projector (DLA-G150CL, JVC Ltd.).
During the functional scans, the projector presented a medium gray screen with the primary purpose to illuminate a participant’s visual field in order to prevent premature fatigue.
[The screen contained a solid black ``fixation'' dot that faded in and out at the beginning and end of a movie segment.]
In the AV study, visual instructions and stimuli were presented on a rear-projection screen using an LCD projector (JVC DLA RS66E, JVC Ltd., light transmission reduced to 13.7\% with a gray filter) connected to the stimulus computer [via a DVI extender system (Gefen EXT-DVI-142DLN with EXT-DVI-FM1000).
The movie was shown at a viewing distance of 63\,cm in 720\,p resolution at full width on a 1280 *1024\,pixel screen with 60\,Hz video refresh rate and screen dimension of 26.5 * 21.2\,cm, corresponding to 23.75*13.5 or 23.75*10.25 when considering only the movie content and excluding the horizontal gray bars].
In both studies [???] auditory stimulation was delivered through an MR confon mkII+ driving custom-built in-ear headphones (HP-M01, MR confon GmbH, Magdeburg, Germany; \citep{baumgart1998electrodynamic}) that reduced the scanner noise by at least 20–30 dB.
Headphones were  fed from an Aureon 7.1 USB (Terratec) sound card through an optical connection.

\subsection{fMRI data acquisition}
\todo[inline]{irrelevantes kürzen}
In both studies, a total of 3599 volumes were recorded for each participant (451, 441, 438, 488, 462, 439, 542 and 338 volumes for movie segment 1–8 respectively).
In AO study, a whole-body 7-Tesla Siemens MAGNETOM magnetic resonance scanner equipped with a local circularly polarized head transmit and a 32 channel brain receive coil (Nova Medical, Inc., Wilmington, MA, USA) acquired T2*-weighted echo-planar images (gradient-echo, 2\,s repetition time (TR), 22\,ms echo time, 0.78\,ms echo spacing, 1488\,Hz/Px bandwidth, generalized autocalibrating partially parallel acquisition, acceleration factor 3, 24 Hz/Px bandwidth in phase encoding direction) using 36 axial slices (thickness 1.4\,mm, 1.4 x 1.4\,mm in-plane resolution, 224\,mm field-of-view, anterior-to-posterior phase encoding direction) with a 10 percent inter-slice gap were recorded in ascending order.
Slices were oriented to include the ventral portions of frontal and occipital cortex while minimizing intersection with the eyeballs. The field-of-view was centred on the approximate location of Heschl's gyrus.
[EPI images were online-corrected for motion and geometric distortions [Oh, S. et al. 2012; In, M. \& Speck, O., 2012; Chung, J. et al., 2011+++]. Auxiliary scans for slice alignment and motion- and distortion-correction were performed at the beginning of the first fMRI recording session and also after the break at the start of the recording for the second half of the movie].
In the AV study, a whole-body 3 Tesla Philips Achieva dStream MRI scanner equipped with a 32 channel head coil acquired T2*-weighted echo-planar images (gradient-echo, 2\,s repetition time (TR), 30\,ms echo time, 90 DEGREE flip angle, 1943\,Hz/Px bandwidth, parallel acquisition with sensitivity encoding (SENSE) reduction factor 2).
35 axial slices (thickness 3.0\,mm, 10\% inter-slice gap) with 80*80 voxels (3.0*3.0 mm of in-plane resolution), 240\,mm mm field-of-view (FoV) and an anterior-to-posterior phase encoding direction were recorded in ascending order.
Philips' ``SmartExam'' was used to automatically position slices in AC-PC orientation such that the topmost slice was located at the superior edge of the brain.

\subsection{Preprocessing}
% DATA SOURCE
\todo[inline]{hier ggf. expliziter erwähnen, dass AO spatially downsampled ist}
% denoised movie data:
% https://github.com/OpenNeuroDatasets/ds001769/tree/master/sub-01/ses-movie/func
fMRI time series data were obtained from
\href{''https://github.com/psychoinformatics-de/studyforrest-data-aligned''}{GitHub}. Data are already aligned to a subject-specific \href{''https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms''}{3 Tesla BOLD template} by a rigid body transformation in MCFLIRT \citep{jenkinson2002registration} to correct for motion during scanning
\citep{sengupta2016extension}.

\todo[inline]{cite sengupta2016 where this was first done and described, ie same image/data was used here}

>>>>

\documentclass[english]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{babel}
\usepackage{svg}
\usepackage{caption, booktabs}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{todonotes}
\usepackage{units}
\usepackage[
	colorlinks=true,
	urlcolor=blue,
	linkcolor=green
]{hyperref}
\newcommand{\scidatalogo}{\includegraphics[height=36pt]{SciData_logo.jpg}}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\setlength{\headheight}{40pt}
\lhead{\textsc{\scidatalogo}}
\usepackage{natbib}

\begin{document}
%\input{descr-stats-ao-events.tex}
%\input{descr-stats-av-events.tex}

@@

\todo[inline]{Vorgabe: Intro + Discussion = main text ~ 3,000 words; einige offene Dinge sind folgend in Kommentaren und nicht als ToDo gemarkt}

@@

Cognitive neuroscientists use brain imaging methods like blood oxygenation level-dependent functional magnetic resonance imaging (BOLD fMRI) to map perceptual and cognitive brain processes (e.g. viewing of landscapes, \citep{epstein1998ppa}; or theory of mind \citep{spunt2014validating}) to functional brain areas or networks.
Brain mapping studies have traditionally employed small sets of carefully chosen, simplified stimuli to strictly control experimental conditions and facilitate functional isolation of brain areas.

@@

Additionally, brain mapping studies have traditionally averaged / usually average results across at least 10-15 subjects to improve the signal-to-noise-ratio (SNR).
The disadvantage here is that the averaging approach does not characterize brain functions at an individual level, a prerequisite for the application of brain imaging methods in individual diagnostics (cf. \citep{dubois2016building})

@@

\todo[inline]{Egal, was ich folgend in der Überblick \& später im Detail bzgl. Aziz (2008) schreibe, es wird wahrscheinlich nicht korrekt sein; so wie ich es verstanden habe, hat Aziz den Unterschied zwischen PPA und FFA angeguckt, aber diesen Unterschied im Kontrast zu object-related Sentences; s. dortige Fig 3; im Grunde kommt da aber überall nur uneinheitliche Grütze raus => bitte gemeinsam im Gespräch checken}

@@

% Aziz hat auf eine zweite Mail geantwortet: Sie modelt die HRF über den jeweils gesamten Satz von ca. 2.8 Sekunden.
% wie oben im Kommentar erwähnt: Ihre Method Section halte ich für etwas strange.Ich zeige dir ganz am Ende mal ihr Paper; hab die entsprechenden Stellen annotiert. Sonst wird hier im Detail Mist erzählt
To our knowledge only one study by \citep{aziz2008modulation} correlated hemodynamic activity of the PPA with spoken sentences.
Sentences described generic or famous places (e.g. ``The Taj Mahal faces a long thin reflecting pool'') or faces  (e.g. ``Marylin Monroe has a large square jaw'').
\todo[inline]{\dots and compared those to a control condition of object-related sentences}
Participants were instructed to press a button whenever the sentence described an inaccurate or improbable fact.
Surprisingly, activation in the left, but not right, PPA was significantly reduced when participants listened to place-related sentences compared to listening to face-related sentences.
Moreover, this effect was only observed in sentences involving famous places.

\todo[inline]{Review von Aminoff (2013) kommt nur kurz als "competing hypothesis"; muss man dann natürlich in der Discussion diskutieren; was aber ggf. gar nicht notwendig ist, weil's darum gar bei uns gar nicht geht}
In summary, studies suggest that the PPA does not exclusively respond to visual(ly) spatial information.
This is consistent with a competing hypotheses stating the PPA does not process the spatial layout of a scene specifically but contextual associations in general (see \citep{aminoff2006parahippocampal} for a review).
Independent(ly) from competing theories (s. \citep{aminoff2013role} for a review), it is still unacknowledged/ uncertain/ indeterminate if auditory stimuli lead to inhibitory or excitatory responses, or no change at all in the PPA.
\todo[inline]{aber Huth, 2016, implizit; diskutiert PPA als solches jedoch gar nicht -> noch mal checken}
\todo[inline]{Coolnessfaktor von naturalistic stimuli ist beinahe komplett raus; Data-driven vs. theory-driven analyses ist komplett raus -> vgl. Speech-Anno-Paper; jedoch in Discussion bringen (s. dort); ggf. erwähnen, dass möglichst ähnliche und nicht fancy analysis gewählt wurde, um Replizierung der Ergebnisse, aber mit naturalistic stimuli zu gewährleisten.}
All revied studies used a just a small set of carefully designed, simplified stimuli to strictly control experimental conditions.
They further relied on / implemented explicit judgment-based tasks to keep participants alert and paying attention.
Thus, they cannot / could answer the question how the PPA might behave under life-like conditions.
Naturalistic stimuli like movies \citep{hasson2008neurocinematics, sonkusare2019naturalistic} or narratives \citep{honey2012not, lerner2011topographic, silbert2014coupled} offer an easy to implement, (continuous,) complex, immersive stimuli that better resemble our experience of a continuous dynamic environment.
Two early studies using naturalistic stimuli suggest functional specialization is preserved during free viewing of a movie when many areas respond simultaneously and interact [+++ der Schlusssatz ist aus hasson und bartels plagiiert \citep{bartels2004mapping, hasson2004intersubject}+++]

% Bartels (2004) und Hasson (2004)
\citep{bartels2004mapping} manually annotated time points that depict faces and human bodies in a 22 minute clip of the movie \textit{Tomorrow Never Dies}.
Employing a general linear model to model hemodynamic activity, these time points correlated with increased activity in the ``fusiform face area'' \citep{kanwisher1997ffa} and ``extrastriate body area'' \citep{downing2001bodyarea} respectively.
Employing a reverse intersubject correlation, \citep{hasson2004intersubject} used a 30 minute clip of the movie \textit{The Good, the Bad, the Ugly}.
fMRI brain volumes showing the highest hemodynamic activity in the PPA [across (five) participants] were matched to the (temporally) corresponding movie frames.
Results revealed that corresponding movie frames depicted indoor and outdoor scenes including buildings and open fields.
Nevertheless, no study investigated how the PPA responds to spatial clues that are embedded in a complex, audio-only stimulus.

\todo[inline]{Bzgl. Open Source der Ergebnisse/Skripte: Dazu habe ich hier nichts geschrieben, weil ich nur weiß, das der Code veröffentlicht werden soll. Du hast die Vision diesbezüglich im Kopf und entsprechend auch kanonisch-prägnante Formulierungen und wo die am besten wie hinkommen}

% Präteritum oder Präsens? Ist momentan gemischt; find's ok so.
% N=14 is inner join of AV & AO
\todo[inline]{The next paragraphs contain a bunch of methods already; reduce this to talk about the general approach:
    a) annotation of events,
    b) investigation of model quality,
    c) cross-analysis of datasets.
    d) Possibly cite https://psyarxiv.com/sdbqv/
    and declare that this study is a concrete realization of that promise
}
In this study, we analyze data of three publicly available datasets from the same set of 14 participants as part of the studyforrest data set (\href{http://www.studyforrest.org}{studyforrest.org}).
We exploratorily investigate how the parahippocampal gyrus [or more general ``human brain''?] responds to ``spatially relevant'' events embedded in a 2h audio-visual movie \citep{hanke2016simultaneous} and its audio-description (i.e. the audio-only variant) of the same length \citep{hanke2014audiomovie}.
We compare these results to PPA localizations that were obtained from a dedicated visual localizer experiment \citep{sengupta2016extension}.

Both natural stimuli were originally designed to entertain an audience and to capture attention free from any perceptual or behavioral task.
We annotated events in the otherwise unknown temporal structure of both stimuli.
In/for the movie, we annotated different kinds of cinematographic cuts \citep{haeusler2016cutanno} as presumably ``spatially relevant'' events.
Our rationale was that cuts re-orient the viewer in the depicted environment independent from the exact visual content in the movie frame following the cut.
In/for the audio-description, we annotated verbal clues about the missing visual content given by the audio-description's additional narrator \citep{haeusler2020speechanno}.

In conformity to the analyses performed in the studies using not-naturalistic stimuli, we employed a standard multi-level, voxel-wise general linear model (GLM) % in order to???
% Practical reasons = Es war viel einfacher nouns der audio-description als Frameinhalt des Films zu annotieren
For practical reasons, and encouraged by \citep{aziz2008modulation} and \citep{aminoff2013role}, we focus on the audio-description as a possible life-like stimulus free from any task to localize a ``visual area'' in individual study participants.

\section{Methods}
\todo[inline]{Specific data outputs should be explicitly referenced via data citation (see Data Records and Data Citations, below)}
\todo[inline]{statement how often datasets have been analyzed be independent groups -> Frage: ist die Liste auf psychoinformatics.de ist aktuell/erschöpfend? Ist dann schnell eingebaut}
We used data from three publicly available datsets as part of the studyforrest dataset (\href{http://www.studyforrest.org}{studyforrest.org}) that has already been used by other research groups for independent research questions before
We used fMRI data from 14 subjects who took part in three different studies. Namely, the same subjects were
a) listening to the audio-description (AO study) \citep{hanke2014audiomovie}) of the movie ``Forrest Gump'', a dataset already used by [XY].
b) watching the actual audio-visual movie (AV study) \citep{hanke2016simultaneous}, a dataset already used by [XY].
c) participating in a dedicated block-wise visual localizer (LOC study) \citep{sengupta2016extension}, a dataset aready used by [XY].
An exhaustive description of the participants, stimulus creation, procedure, stimulation setup, and fMRI acquisition can be found in the corresponding publications  \citep{hanke2014audiomovie, hanke2016simultaneous, sengupta2016extension}.
Following is a brief summary of most important aspects.
\todo[inline]{um Sengupta ergänzen}

\subsection{Participants}
\todo[inline]{ich habe von den aligned data eine Intersection von 14 VPN aus AO und AV; in der Speech-Anno-Validation (7T only) habe ich 19 VPN; es fehlt jeweils VP10; demographische Daten bzgl. (Durchschnitts)Alter und Geschlecht ist folglich falsch}
In the AO study, 19 participants (all right-handed, age 21–38 years, mean age 26.6 years, 12 male) listened to the German audio-description \citep{ForrestGumpGermanAD} of the movie ``Forrest Gump'' \citep{ForrestGumpMovie} as an additional audio track for visually impaired listeners on Swiss public television.
In the AV study, the same 14 participants [+++VP 10 wurde nicht genutzt+++] (21–39 years, mean age 29.4, six female) watched the audio-visual movie with dubbed German audio track \citep{ForrestGumpDVD}.

\todo[inline]{Daten zu Sengupta einarbeiten}
In the LOC study\dots

@@

\subsection{Stimuli}
We used the German DVD release \citep{ForrestGumpDVD} of the audio-visual movie ``Forrest Gump'' \citep{ForrestGumpMovie} and its temporally aligned audio-description (i.e. the audio-only variant of the movie) that was broadcast as an additional audio track for visually impaired listeners on Swiss public televinsion \citep{ForrestGumpGermanAD}.
The plot of the movie is already carried by an off-screen voice of the main character Forrest Gump.
In the largely identical audio-description, a male narrator additionally describes essential aspects of the visual scenery when there is no off-screen voice, dialog, or other relevant auditory content.
The audio-description was temporally aligned to the audio track of the German DVD release. A few scenes less relevant to the major plot were removed to create the ``research cut'' lasting $\approx$2h \citep{hanke2014audiomovie,hanke2016simultaneous}.
Both stimuli were further processed (filtering, volume adjustments) to improve audibility during MRI scanning.
Finally, each stimulus was split into eight segments of approximately 15 minutes.
Except for the first movie segment, each segment started with a snippet of at least six seconds immediately preceding the movie scene boundary used to split the segments (s. Figure 3a in \citep{hanke2014audiomovie}.
\todo[inline]{Sengupta: Stimuli}
% LOC study?

\subsection{Stimulus Annotation}
% Kategorie ``++'' enthält ausnahmesweise auch adverbiale Best. der Zeit.
\todo[inline]{WARUM WAS WIE annotiert wurde}
\todo[inline]{aus Speech-Anno Paper 'descriptive-statistics-anno.py' übernehmen \& anpassen, um Statistiken und runcommand-file zu erstellen}
We extended a publicly available annotation of speech \citep{haeusler2020speechanno} by manually annotating the audio-description's narrator:
Two persons performed a categorization of nouns embedded in sentences spoken by the narrator to describe the movie's missing visual content.
\todo[inline]{Warum wurden diese Kategorien so gewählt}
\todo[inline]{Maybe just cite the table}
The nouns were categorized by the clue they provide about the cinematographic scene's environment (geo, geo-room; setting\_new, setting\_old), its inherent persons (female, female name; male, male name, person), a person's appearance (face, head; body, bodypart), and a scene's inherent objects (object, furniture).
See Table \ref{tab:descr-nouns} for a complete overview of all cateogries, [+++rules, counts, examples].

A preliminary annotation by one person according to the rules [entweder im laufenden Text oder in einer [eigenständigen] Tabelle]. Minor corrections due to incorrectly applied rules were by the author.

@@

\subsection{Stimulation setup}
\todo[inline]{irrelevantes kürzen}
In both studies, stimulation was implemented with \href{http://www.psychopy.org}{PsychoPy} \citep{peirce2007psychopy} running on a computer with the \href{http://neuro.debian.net}{(Neuro)Debian} operating system \citep{halchenko2012open}.
In the AO study, visual instructions were presented on a rear-projection screen inside scanner bore using an LCD projector (DLA-G150CL, JVC Ltd.).
During the functional scans, the projector presented a medium gray screen with the primary purpose to illuminate a participant's visual field in order to prevent premature fatigue.
[The screen contained a solid black ``fixation'' dot that faded in and out at the beginning and end of a movie segment.]

In the AV study, visual instructions and stimuli were presented on a rear-projection screen using an LCD projector (JVC DLA RS66E, JVC Ltd., light transmission reduced to \unit[13.7]{\%} with a gray filter) connected to the stimulus computer [via a DVI extender system (Gefen EXT-DVI-142DLN with EXT-DVI-FM1000).
The movie was shown at a viewing distance of \unit[63]{cm} in \unit[720]{p} resolution at full width on a \unit[1280 $\times$ 1024]{pixel} screen with \unit[60]{Hz} video refresh rate and screen dimension of \unit[26.5 $\times$ 21.2]{cm}, corresponding to \unit[23.75 $\times$ 13.5] or \unit[23.75 $times$ 10.25]{cm} when considering only the movie content and excluding the horizontal gray bars.

In both studies [+++???+++] auditory stimulation was delivered through an MR confon mkII+ driving custom-built in-ear headphones (HP-M01, MR confon GmbH, Magdeburg, Germany; \citep{baumgart1998electrodynamic}) that reduced the scanner noise by at least \unit[20–30]{dB}.
Headphones were  fed from an Aureon 7.1 USB (Terratec) sound card through an optical connection.

\subsection{fMRI data acquisition}
\todo[inline]{irrelevantes kürzen}
In both studies, a total of 3599 volumes were recorded for each participant (451, 441, 438, 488, 462, 439, 542, and 338 volumes for movie segment 1–8 respectively).

In the AO study, a whole-body \unit[7]{Tesla} Siemens MAGNETOM magnetic resonance scanner equipped with a local circularly polarized head transmit and a 32 channel brain receive coil (Nova Medical, Inc., Wilmington, MA, USA) acquired T2*-weighted echo-planar images
(gradient-echo, \unit[2]{s} repetition time (TR), \unit[22]{ms} echo time, \unit[0.78]{ms} echo spacing, \unit[1488]{Hz/Px} bandwidth, generalized autocalibrating partially parallel acquisition, acceleration factor 3, \unit[2]{Hz/Px} bandwidth in phase encoding direction) using 36 axial slices (thickness \unit[1.4]{mm}, \unit[1.4 $\times$ 1.4]{mm} in-plane resolution, \unit[224]{mm} field-of-view, anterior-to-posterior phase encoding direction)
with a 10 percent inter-slice gap were recorded in ascending order.
Slices were oriented to include the ventral portions of frontal and occipital cortex while minimizing intersection with the eyeballs.
The field-of-view was centred on the approximate location of Heschl's gyrus.
[+++EPI images were online-corrected for motion and geometric distortions [Oh, S. et al. 2012; In, M. \& Speck, O., 2012; Chung, J. et al., 2011].
[Auxiliary scans for slice alignment and motion- and distortion-correction were performed at the beginning of the first fMRI recording session and also after the break at the start of the recording for the second half of the movie].

In the AV study, a whole-body \unit[3]{Tesla} Philips Achieva dStream MRI scanner equipped with a 32 channel head coil acquired T2*-weighted echo-planar images (gradient-echo, \unit[2]{s} repetition time (TR), \unit[30]{ms} echo time, \unit[90]{$^{\circ}$} flip angle, \unit[1943]{Hz/Px} bandwidth, parallel acquisition with sensitivity encoding (SENSE) reduction factor 2).
35 axial slices (thickness \unit[3.0]{mm}, \unit[10]{\%} inter-slice gap) with \unit[80 $\times$ 80]{voxels} (\unit[3.0 $\times$ 3.0]{mm} of in-plane resolution), \unit[240]{mm} field-of-view ) and an anterior-to-posterior phase encoding direction were recorded in ascending order.
Philips' ``SmartExam'' was used to automatically position slices in AC-PC orientation such that the topmost slice was located at the superior edge of the brain.

\subsection{Preprocessing}
% data source
\todo[inline]{wie immer bzgl. Motion Correction und Registratziohier ggf. expliziter erwähnen, dass AO spatially downsampled ist}
\todo[inline]{cite sengupta2016 where this was first done and described, ie same image/data was used here}
fMRI time series data were obtained from
\href{https://github.com/psychoinformatics-de/studyforrest-data-aligned}{GitHub}.
Data are already aligned to a subject-specific \href{https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms}{3 Tesla BOLD template} by a rigid body transformation in MCFLIRT \citep{jenkinson2002registration} to correct for motion during scanning
\citep{sengupta2016extension}.

% preprocessing intro
All further analysis steps in the current study were carried out using tools of FSL v5.0.9 (\href{https://www.fmrib.ox.ac.uk/fsl}{FMRIB's Software Library};\citep{smith2004fsl}; on a computer cluster running the \href{https://www.debian.org}{Debian} GNU/Linux operating system.
Software packages were obtained from repositories of \href{http://neuro.debian.net}{NeuroDebian} \citep{halchenko2012open}.
